Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-13 analysis/paper/Rmd/hotspots-paper.Rmd
switched to eval = TRUE for git2r call
removed dependencies on git2r (and on libgit2 library)
fixed inline code

This report was generated on ` r Sys.time()` using the following computational environment and dependencies:

@@

```{r git2r, cache = FALSE, echo = TRUE}
# what commit is this file at?
git2r::repository(here::here())
```

>>>>

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

@@

```{r git2r, cache = FALSE, echo = TRUE, eval = FALSE}
# what commit is this file at?
git2r::repository(here::here())
```
